\makenoidxglossaries

%\newacronym{radar}{RADAR}{Radio Detection and Ranging}

\newglossaryentry{blocking call}{
	name=blocking call, 
	description={an operation that causes an executing thread or process to wait until a specific condition is met or an even occurs before it can proceed.}
}

\newglossaryentry{bottleneck}{
	name=bottleneck, 
	description={a point in the system where the performance or capacity is siginificantly limited, slowing down the overall throughput and efficiency of the system.}, 
	firstplural={\glsentryplural{bottleneck}} 
}

\newglossaryentry{thread}{
	name=thread,
	description={the smallest sequence of programmed instructions that can be managed independently by a scheduler as a component of a process.},
	firstplural={\glsentryplural{thread}}
}

\newglossaryentry{overhead}{
	name=overhead,
	description={any combination of excess or indirect computation time, memory, bandwidth, or other resources that are required to perform a specific task.}, 
	firstplural={\glsentryplural{overhead}}
}

\newglossaryentry{propagation delay}{
	name={propagation delay},
	description={the amount of time required for a signal to be received after it has been sent.}
}

\newglossaryentry{handshaking}{
	name=handshaking, 
	description={an automated process of negotiation between two participants (example two CPU devices) through the exchange of information that establishes the protocols of a communication link at the start of the communication, before full communication begins}
}

\newglossaryentry{MPI}{
	name=MPI, 
	description={(Message Passing Interface) a message-passing standard designed to function on distributed parallel computing architectures.}
}

\newglossaryentry{MMU}{
	name=MMU, 
	description={a part of a computer's hardware archeticture that handles all memory and caching operations associated with the processor.}
}

\newglossaryentry{shared memory}{
	name=shared memory, 
	description={an parallel system feature that allows processor tasks to share data by having shared access to pools of memory.}
}

\newglossaryentry{distributed memory}{
	name=distributed memory, 
	description={a model in which each processor has its own memory and tasks must communicate with remote processors to transfer data.}
}

\newglossaryentry{Lexically}{
	name=Lexically, 
	description={ordered alphebatically},
}

\newglossaryentry{critical section}{
	name=critical section, 
	description={the part of a multi-task program that must not be concurrently executed by more than one process.},
}

\newglossaryentry{serialization}{
	name=serialization, 
	description={converting a process so that it is executed sequentially.},
}

\newglossaryentry{mutex}{
	name=mutex, 
	description={or \textit{mutual exclusion} is a program object that prevents multiple threads from accessing the same shared resource simultaneously.},
}

\newglossaryentry{mux}{
	name=mux, 
	description={or \textit{multiplexer} is a device that can receive multiple input signals and synthesize a single output signal in a recoverable manner for each input signal.},
}

\newglossaryentry{Xilinx}{
	name=Xilinx, 
	description={company known for inventing the first commercially viable FPGA.},
}

\newglossaryentry{CMOS inverter}{
	name=CMOS inverter, 
	description={is a device that is used to generate logic functions and is the essential component in all integrated circuit applications.},
}

\newglossaryentry{bus}{
	name=bus, 
	description={a collection of signal lines with a linked purpose and through which data can be transferred.},
}

\newglossaryentry{state machine}{
	name=state machine, 
	description={a behavioural model which shows the changes that the current state undergoes given an input.},
	firstplural={\glsentryplural{state machines}}
}

\newglossaryentry{endianness}{
	name=endianness, 
	description={is the order in which bits within a word of digital data are arranged.},
}

\newglossaryentry{watchdog}{
	name=watchdog, 
	description={is an electronic or software timer that is used to detect and recover from computer malfunctions.},
}

\newglossaryentry{OpenML}{
	name=OpenML, 
	description={is an open platform for sharing datasets, algorithms, and experiments - to make machine learning and data analysis simple, accessible, collaborative and open with an optimal division of labour between computers and humans.},
}

\newglossaryentry{global memory}{
	name=global memory, 
	description={is a memory address space that can be accessed by all processes across all blocks.},
}

\newglossaryentry{semaphore}{
	name=semaphore, 
	description={is a synchronization primitive that can be used as a form of message-passing control to allow processes to synchronize access to shared memory or memory-mapped files.},
	firstplural={\glsentryplural{semaphores}}
}

\newglossaryentry{race condition}{
	name=race condition, 
	description={occurs when two processes attempt to access the same resource or memory location at the same time, leading to errors.},
	firstplural={\glsentryplural{race conditions}}
}

\newglossaryentry{threads model}{
	name=threads model, 
	description={uses concepts of the shared memory architecture where a primary process can run multiple lightweight concurrent execution paths.},
	firstplural={\glsentryplural{thread models}}
}

\newglossaryentry{CUDA}{
	name=CUDA, 
	description={is a parallel computing platform and programming model developed by NVIDIA for general computing on GPUs.},
}

\newglossaryentry{pragma}{
	name=pragma, 
	description={a section of code that is to be executed in parallel and is marked by a special directive (omp pragma).},
	firstplural={\glsentryplural{pragma}}
}

\newglossaryentry{work-item}{
	name=work-item, 
	description={unit of an OpenCL program's organised grid of work group.},
	firstplural={\glsentryplural{work item}}
}

\newglossaryentry{data parallel}{
	name=data parallel, 
	description={ability to distribute data across different nodes in a parallel execution environment.},
	firstplural={\glsentryplural{work item}}
}

\newglossaryentry{PC}{
	name=PC, 
	description={personal computer.},
}

\newglossaryentry{superscalar execution}{
	name=superscalar execution, 
	description={the CPU manages multiple instruction pipelines to execute several instructions concurrently during a clock cycle.},
}

\newglossaryentry{out-of-order execution}{
	name=out-of-order execution, 
	description={a CPU paradigm in which a processor executes instructions in an order based on availability of input data/instructions rather than the original order in a program.},
}

\newglossaryentry{throughput}{
	name=throughput, 
	description={A measure of the volume of data that passes through a network in a given period.},
}

\newglossaryentry{static code analysis}{
	name=static code analysis, 
	description={is a code quality inspection and bug finding method typically done as a manual code review by not running the code but reading over the code.},
}

\newglossaryentry{IDE}{
	name=IDE, 
	description={integrated development environment.},
}

\newglossaryentry{birefringence}{
	name=birefringence, 
	description={is the phenomenon exhibited by certain materials in which a single incident ray of light is split into two rays traveling in different directions},
	firstplural={\glsentryplural{birefringence}}
}

\newglossaryentry{high-finesse}{
	name=high-finesse, 
	description={of an optical resonator (cavity) refers to sharp resonances in relation to the frequency distances for light that is circulating in the resonator in the absence of an external field},
	firstplural={\glsentryplural{high-finesse}}
}

\newglossaryentry{ancilla}{
	name=ancilla, 
	description={qubits are extra qubits that are added to ensure that a computation is irreversible},
	firstplural={\glsentryplural{ancilla}}
}

\newglossaryentry{crosstalk}{
	name=crosstalk, 
	description={is the undesirable coupling of qubits that can lead to degradationin the performance of a quantum circuit},
	firstplural={\glsentryplural{crosstalks}}
}

\newglossaryentry{interferometer}{
	name=interferometer, 
	description={is an analytical instrument that works by combining or splitting beams of light to create an interefernce pattern},
	firstplural={\glsentryplural{interferometers}}
}

\newglossaryentry{piezo-actuated}{
	name=piezo-actuated, 
	description={is the characteristic of a device of having movement that is enabled by the piezoelectric effect},
	firstplural={\glsentryplural{piezo-actuated}}
}

\newglossaryentry{polarimeter}{
	name=polarimeter, 
	description={is an analytical device for determining the polarisation properties of light beams and samples},
	firstplural={\glsentryplural{polarimeters}}
}

\newglossaryentry{personality}{
	name=personality, 
	description={of an FPGA is the program that is interwoven into the logic structure of the device},
	firstplural={\glsentryplural{personalities}}
}

\newglossaryentry{hyperfine structure}{
	name=hyperfine structure, 
	description={is defined by the shifts in degenerate electronic energy levels due to electronic spin which splits the energy levels into several equal levels},
}


\newglossaryentry{fine-grained}{
	name=fine-grained, 
	description={problems are divided into a large number of smaller tasks such that each computation in the solution is highly dependent on other parts of the problem space.},
}

\newglossaryentry{co-prime}{
	name=co-prime, 
	description={numbers are pairs of numbers that do not share a common factor other than 1},
}

\newglossaryentry{NP-complete}{
	name=NP-complete, 
	description={problems are a class of problems which have solutions that can be quickly checked on a classical computer},
}

\newglossaryentry{unitary operation}{
	name=unitary operation, 
	description={refers to a mathematical operation that preserves the norm of a quantum state},
	firstplural={\glsentryplural{unitary operations}}
}

\newglossaryentry{quantum state}{
	name=quantum state, 
	description={a mathematical representation that describes the properties of a system of quantum particles such as electrons and photons},
	firstplural={\glsentryplural{quantum states}}
}

\newglossaryentry{quantum gate}{
	name=quantum gate, 
	description={refers to the basic operation in a quantum computing that changes the state of qubits},
	firstplural={\glsentryplural{quantum gates}}
}

\newglossaryentry{quantum annealing}{
	name=quantum annealing, 
	description={is a process that uses quantum fluctuations for optimising allocations of the global minimum of a given objective function over a given set of candidate solutions},
	firstplural={\glsentryplural{quantum annealings}}
}

\newglossaryentry{quantum dot}{
	name=quantum dot, 
	description={is a semiconductor nanocrystal that confines the motion of conduction band electrons, valence band holes or excitons in all three spatial directions},
	firstplural={\glsentryplural{quantum dot}}
}

\newglossaryentry{mantissa}{
	name=mantissa, 
	description={is the part of a number located after a decimal point which dictates the precision of a fractional number},
	firstplural={\glsentryplural{mantissas}}
}

\newglossaryentry{fiducial state}{
	name=fiducial state, 
	description={a quantum state that can be reproduced with low variability},
	firstplural={\glsentryplural{fiducial states}}
}